\documentclass[9pt]{scrbook} 

\usepackage[utf8]{inputenc} 
\usepackage[a4paper]{geometry} 
\usepackage[dvipsnames,table]{xcolor}
\usepackage{eurosym}
\usepackage{sectsty}
\usepackage{tabularx,booktabs}
\usepackage{fancyhdr}
\usepackage{makecell}
\usepackage[colorlinks=true, 
			linkcolor=NavyBlue, 
			citecolor=NavyBlue, 
			urlcolor=NavyBlue]{hyperref} 

% Geometry
\setlength{\hoffset}{-18pt}        
\setlength{\oddsidemargin}{0pt} 
\setlength{\evensidemargin}{9pt} 
\setlength{\marginparwidth}{54pt} 
\setlength{\textwidth}{481pt} 
\setlength{\voffset}{-18pt} 
\setlength{\marginparsep}{7pt} 
\setlength{\topmargin}{0pt} 
\setlength{\headheight}{0em} 
\setlength{\headsep}{0pt} 
\setlength{\footskip}{50pt} 
\setlength{\textheight}{708pt} 
\setlength{\parindent}{0cm}

% Settings
\pagestyle{fancy} 
\lhead{}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}
\allsectionsfont{\sffamily\mdseries\upshape}
\cfoot{ \sffamily \thepage /3}
\linespread{1.2}
\font\sb=ec-lmssdc10 at 9pt
\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\headrulewidth}{0pt} 
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{M}[1]{>{\raggedright}p{#1}}


\begin{document}


% Top right
\parbox[][4.5cm][t]{16.3cm}{ 
\begin{flushright}
{\LARGE Léonard Seydoux}\\
PhD student in Seismology\\
Institut de Physique du Globe de Paris\\
1 rue Jussieu 75005 Paris, France\\
{\href{mailto:seydoux@ipgp.fr}{\slshape seydoux@ipgp.fr}\\
+331 83 95 75 43\\
French, 27 years old}
\end{flushright}
}


\begin{tabularx}{\textwidth}{R{7em}ll}
& {\Large\bfseries Education} \\[0.7em]
\Xhline{0.7pt} \\


\textcolor{gray}{\sb 2013-16} & \textbf{Ph.D. in Seismology} -- Institut de Physique du Globe de Paris, France\\
\textcolor{gray}{\sb 2011-13} & \textbf{M.S. in Acoustics} -- Université Pierre et Marie Curie, Paris 6, France\\
\textcolor{gray}{\sb 2007-11}  &  \textbf{B.S. in Physics} -- Université Paul Sabatier, Toulouse 3, France\\
\end{tabularx} 
\vspace{3em}





\begin{tabularx}{\textwidth}{R{7em}ll}
& {\Large\bfseries Teaching} \\[0.7em]
\Xhline{0.7pt} \\

& {Total teaching hours as teacher assistant: $\sim$200 h.} \\
& {Paris Diderot University and Institut de Physique du Globe de Paris, Paris, France}\\[1em]
\textcolor{gray}{\sb Bachelor}& Python programming (20 h)\\
& Data analysis in Earth sciences (60 h)\\
& Experimental Physics with Python and Arduino (24 h)\\
& Office automation (44 h)
& \\[1em]
\textcolor{gray}{\sb Master}& Matlab programming (44 h) \\
& C/C++ programming practicals (12 h)
\end{tabularx} 
\vspace{3em}




\begin{tabularx}{\textwidth}{R{7em}ll}
& {\Large\bfseries Other activities} \\[0.7em]
\Xhline{0.7pt} \\

\textcolor{gray}{\sb 2016 (6 mth)} &  \parbox[t]{0.8\textwidth}{\textbf{Master student internship supervizing:} Dr. Jean Soubestre, Institut de Physique du Globe de Paris, Laboratoire de Sismologie. \textit{A study of the volcanic activity of the Klyuchevskoy group of volcano (Kamchatka) with array processing methods.} \\{\small \slshape Duration: 6~months. Supervisor: Nikolaï Shapiro (Institut de Physique du Globe de Paris).}}\\[5em] 

\textcolor{gray}{\sb Mar. 2016} & \parbox[t]{0.8\textwidth}{\textbf{Open Classroom at University:} \textit{Music to understand string motion}. {\small Paris Diderot University.  Organizers: Dr. Lambert Caron and Dr. Arnaud Burtin, Institut de Physique du Globe de Paris. Duration:~1~day. Participants:~$\sim$40~bachelor students.}}\\[4em]

\textcolor{gray}{\sb Oct. 2014} & \parbox[t]{0.8\textwidth}{\textbf{Scientific days organization:} \textit{Seismology and tectonics on Earth: from the large scale behaviour to the impact on urban constructions}. {\small Institut de Physique du Globe de Paris. Duration:~3~days. Visitors:~$\sim$80~students from middle and high school, and general public.}}\\[4em]

\textcolor{gray}{\sb  Mar. 2014} &  \parbox[t]{0.8\textwidth}{{\bfseries IPGP PhD meeting organization:} Website development, communication manager and program comity (\url{https://hekla.ipgp.fr/cdd2014/index.php?page=home}). {\small Meeting duration:~1~week. Participants:~180~PhD students from IPGP + 12~external PhD students. Budget:~15000\euro{}}}
\end{tabularx}


\begin{tabularx}{\textwidth}{R{5em}ll}
& {\Large\bfseries Publications} \\[0.7em]
\Xhline{0.7pt} \\[2em]

& {\bfseries Peer-reviewed journals (3 published, 1 in preparation)}\\[1em]

\textcolor{gray}{\sb in prep.} & \small \parbox[t]{0.8\textwidth}{\textbf{Seydoux, L.}, Shapiro, N. M., de Rosny, J. (exp. 2016/2017). {\itshape Pre-Processing Noise Cross-Correlations with Equalizing the Network Covariance Matrix Eigen-Spectrum.} To be submitted. }\\[2.5em]

\textcolor{gray}{\sb 2016} & \small \parbox[t]{0.8\textwidth}{\textbf{Seydoux, L.}, Shapiro, N. M., de Rosny, J., \& Landes, M. (2016). {\itshape Spatial coherence of the seismic wavefield continuously recorded by the USArray.} Geophysical Research Letters, 43, 9644 -- 9652. \url{http://doi.org/10.1002/2016GL070320}}\\[3.5em]

\textcolor{gray}{\sb 2016} & \small \parbox[t]{0.8\textwidth}{\textbf{Seydoux, L.}, Shapiro, N. M., de Rosny, J., Brenguier, F., \& Landes, M. (2016). {\itshape Detecting seismic activity with a covariance matrix analysis of data recorded on seismic arrays.} Geophysical Journal International, 204(3), 1430–1442. \url{http://doi.org/10.1093/gji/ggv531}}\\[3.5em]


\textcolor{gray}{\sb 2014} & \small \parbox[t]{0.8\textwidth}{Le Carrou, J. L., Chadefaux, D., {\bfseries Seydoux, L.}, \& Fabre, B. (2014). {\slshape A low-cost high-precision measurement method of string motion.} Journal of Sound and Vibrations. \url{http://doi.org/10.1016/j.jsv.2014.04.023}}\\[5em]

& {\bfseries Conferences proceedings (1 talk, 2 posters)}\\[1em]


\textcolor{gray}{\sb 2016} & \small \parbox[t]{0.8\textwidth}{\textbf{Seydoux, L.}, de Rosny, J., \& Shapiro, N. M. (2016, December). {\slshape Pre-Processing Noise Cross-Correlations with Equalizing the Network Covariance Matrix Eigen-Spectrum.} In 2016 AGU Fall Meeting (poster).}\\[3.5em]

\textcolor{gray}{\sb 2015} & \small \parbox[t]{0.8\textwidth}{\textbf{Seydoux, L.}, Shapiro, N. M., de Rosny, J., \& Landes, M. (2015, December). {\slshape A Spatial Coherence Analysis of Seismic Wavefields Based on Array Covariance Matrix: Application to One Year of the USArray Data.} \href{https://agu.confex.com/agu/fm15/webprogram/Paper59436.html}{In 2015 AGU Fall Meeting} (talk).}\\[3.5em]


\textcolor{gray}{\sb 2014} & \small \parbox[t]{0.8\textwidth}{\textbf{Seydoux, L.}, Shapiro, N., de Rosny, J., \& Brenguier, F. (2014, December). {\slshape Detecting Seismic Activity with a Covariance Matrix Analysis of Data Recorded on Seismic Arrays.} \href{http://adsabs.harvard.edu/abs/2014AGUFM.S41A4407S}{In AGU Fall Meeting Abstracts (Vol.1, p.4407)}, (poster).}\\[5em]


& {\bfseries Invited seminars} \\[1em]
\textcolor{gray}{\sb 2016} & Invited seminar at the {\slshape Institut des Sciences de la Terre}, Grenoble, France.\\
\textcolor{gray}{\sb 2016} & Invited seminar at the {\slshape Laboratoire de Planétologie et Géodynamique}, Nantes, France.\\
\textcolor{gray}{\sb 2014} & Invited seminar at the {\slshape Laboratoire d'Imagerie Paramétrique}, UPMC, Paris, France.\\[2em]


& {\bfseries Other presentations} \\[1em]

\textcolor{gray}{\sb 2016} & \small \parbox[t]{0.8\textwidth}{\textbf{Seydoux, L.}, Shapiro, N., de Rosny (2015, March). {\slshape A new approach to spatial coherence analysis of the wavefield recorded by seismic arrays : application to one year of data from the USArray.} \href{https://hekla.ipgp.fr/cdd2016/tmp/abstract112.pdf}{In IPGP PhD Meeting, Paris 2016} (talk).}\\[3.5em]

\textcolor{gray}{\sb 2015} & \small \parbox[t]{0.8\textwidth}{\textbf{Seydoux, L.}, Shapiro, N., de Rosny, J., \& Brenguier, F. (2015, May). {\slshape Detecting Seismic Activity with a Covariance Matrix Analysis of Data Recorded on Seismic Arrays.} \href{https://isterre.fr/research-28/teams/waves-and-structures/ambient-noise-imaging-and-monitoring-workshop-cargese-2015}{In Ambient Noise Imaging and Monitoring Workshop, Carg\`ese 2015} (poster).}\\[3.5em]

\textcolor{gray}{\sb 2015} & \small \parbox[t]{0.8\textwidth}{\textbf{Seydoux, L.}, Shapiro, N., de Rosny, J., Brenguier, F. \& Land\`es M. (2015, March). {\slshape Detecting Seismic Activity with a Covariance Matrix Analysis of Data Recorded on Seismic Arrays.} \href{https://hekla.ipgp.fr/cdd2015/tmp/abstract1067.pdf}{In IPGP PhD Meeting, Paris 2015} (poster).}\\[3.5em]

\textcolor{gray}{\sb 2014} & \small \parbox[t]{0.8\textwidth}{\textbf{Seydoux, L.}, Shapiro, N., de Rosny, J., Brenguier, F. \& Land\`es M. (2014, March). {\slshape Detecting Seismic Activity with a Covariance Matrix Analysis of Data Recorded on Seismic Arrays.} \href{https://hekla.ipgp.fr/cdd2014/tmp/abstract1067.pdf}{In IPGP PhD Meeting, Paris 2014} (poster).}


\end{tabularx} 









\begin{tabularx}{\textwidth}{R{7em}ll}
& {\Large\bfseries Skills} \\[0.7em]
\Xhline{0.7pt} \\
\textcolor{gray}{\sb Programming}& {\ttfamily Python} (package development), {\ttfamily MATLAB}, {\ttfamily C/C++}\\[0.5em]
\textcolor{gray}{HPC} & {\ttfamily MPI}, {\ttfamily OpenMP}, {\ttfamily SLURM}\\[0.5em]
\textcolor{gray}{\sb Geosciences}& Axisem, Tau-p, Generic Mapping Tools \\[0.5em]
\textcolor{gray}{\sb Operating systems}& Unix (any distribution), Macintosh, Windows  \\[0.5em]
\textcolor{gray}{\sb Web development} &  HTML, CSS, PHP, SQL\\[0.5em]
\textcolor{gray}{\sb Other softwares} & \parbox[t]{0.8\textwidth}{Latex, Github, Office suite and equivalents, Adobe Creative Suite and equivalents}\\[0.5em]
\textcolor{gray}{\sb Languages} & French (native), English (fluent), Spannish (good notions)\\[0.5em]
\textcolor{gray}{\sb Other}& Driving licence \\
& Autonomous diver (CMAS international level 2)\\
& Music education \\
\end{tabularx} 









\end{document}